\section{Business plan}
	\subsection{introduction}
	We take a responsible approach to finding sponsors. And also try to spend money effectively advance thinking through the details and equipment, finding ways to get them maximum benefit. Some sets we received as prizes in competitions.
	
	\subsection{Our sponsors and their support}
		\subsubsection{PTC and Irisoft}
		PTC and Irisoft representative in Russia is the one company that has helped us to begin to engage FTC. They provided us the first set of Tetrx within the program's Score Thehnic which involved our Lyceum. They provide us with a different command symbols plus small gifts for other teams. They help us with the delivery of details from U.S.A. We use them programa Creo for creating 3D models. We also take part in events organized by them.
		\subsubsection{Robofinist}	
		Robofinist Charitable Foundation organized by Temur Amindzhanov and by Starline. They offered us its assistance as an organization in our city with outstanding achievements. They help to financially each month to give us 2000 Dolars, parts and equipment.
		\subsubsection{Volnoe Delo}
		Volnoe Delo is one of the largest charitable foundations in Russia. It was established by Oleg Deripaska. We are participants of the program ROBOTOTEHNIKA.As support they sent us free game field.They also engaged in training teachers and judges, including our own.They engaged in the organization of competitions FTC in Russia and are sponsoring a trip this year's winners to St. Louis.	
		\subsubsection{Physics-Mathematics Lyceum №30}
		Physics-Mathematics Lyceum №30 is a school in which is our organization. It provides us with a comfortable space and material assistance, as well as leaders.
		
	\subsection{Purchase of materials.}
		\subsubsection{Our method}
		When we started robotics we had not a lot of money and we used only some basic materials. Now we found sponsors and firstly plan the details and equipment that we need to buy and then buy them.Such an approach allows us to find more effective solutions.
		\subsubsection{Our materials}
		We have 6 primary kits and 3 resource kits.We buy individual parts we need.At this point was made 2 large purchases from U.S.A for 1600 Dolar in November 2014 and March 2015.
\newpage	