\subsubsection{"Robofest-Ryazan" (19-20 of December)}
The team members who were in this competition:
\begin{enumerate}
	\item Evgeniy Maksimychev: programmer, operator 
	
	\item Timur Babadzhanov: public relation, operator 
\end{enumerate}
\paragraph{19 of December}
Today there were training matches
\begin{itemize}
	\item Wiring for servos finished. Servos set up.
	
	\item Gripper with speed transmission 1:2 tested. It was found that it can't grip elements because brush is too rigid and the motor can't turn. So it was decided to make transmission 1:1.
	
	\item Also we debuged the program for autonomous period that scores climbers.
	
	\item During the trainings of teleop period it was found that robot still couldn't climb the ramp. The robot could reach the first churro but after that it slipped down. We didn't understand why it happened. To solve this problem we tried to remove the treads from the back wheels. We thought that it lifted them and the distance that robot must rise for climbing to first churro would reduce. But it was not enough. So during the matches we scored only to low box.
	
	\item Also we communicated with other teams. There were 3 teams (not counting ours). Nobody had a program for the autonomous period and nobody was able to score debris to boxes.
\end{itemize}
\paragraph{20 of December}
Today there were qualifying and final matches.\newline
We won 3 of 4 qualifying matches. One match we lost because the chain on the wheels base came off. So we became 3 by the results of qualifying matches and played final match and won it.\newline
Summary:
\begin{enumerate}
	\item During matches we scored about 10 debris for match (worse than in "Robofest-South").
	
	\item There was a problem that chain on wheel base came off. Maybe that's due to bias of it. Other mechanisms worked stably.
	
	\item In addition we saw competitions or RC cars and payed attention on their wheels. They are very soft. Maybe if we install similar wheels on our robot it would help us climb the mountain. They will bend when robot gets to the churro and so robot don't get stuck, as with rigid wheels.  
\end{enumerate}
\fillpage
