\subsubsection{"Robofest-South" (5-6 of December)}
The team members who were in this competition:
\begin{enumerate}
	\item Evgeniy Maksimychev: programmer, operator 
	
	\item Timur Babadzhanov: public relation, operator 
\end{enumerate}
\paragraph{5 of December} 
Today there were trainings and judging.
\begin{itemize}
	\item This day we made autonomous period for these actions: ride to shelter, score climbers and stay at repair zone. It give us 45 points (2x(10 + 10) - climbers for autonomous and teleop 5 - robot in repair zone). During this process it was found that robot can't move on a straight line accuratly with one encoder due to different tensions of the chain in different sides of the robot. So we decided to remove the wire for encoder from the motor that turned the lift and connect the second encoder to the wheel base. Then we wrote a proportional regulator that gave more power to motor that turned a smaller angle than the others. It allowed to solve this problem. Also it was found that cubes and balls can prevent to working of the robot during autonomous period. So we added intake rotation that would repel debris. But if the intake rotated faster it would work better. So we needed to install a transmission for increasing speed.
	\item Also today operators trained on the robot control. We reached the next result: full low box and scored buttom climber in 2 minutes.
	\item In addition we communicated with other teams. There are 13 teams in this competition (including our team). It was found that we are the only team that can score into low box. The rest of the teams are able to score debris into floor goal and 2-3 teams can score button climbers. Also about five teams can climb to low zone of mountain and one to the middle.
\end{itemize}
\paragraph{6 of December} 
Today there were qualifying and final matches.\newline
Qulifying mathes (3 mathes):
\begin{enumerate}
	\item First match. In automous period we got 5 points (didn't score climbers, ally hadn't automous). In teleop period we didn't score debris because we hadn't charged our battery so our lift didn't work. Our ally scored about 7 elements to floor goal. We lost this match.
	\item Second match. 5 points for autonomous (the same situation as in first match). In teleop we scored 10 elements to low box and pushed buttom climber. Our ally scored about 10 - 12 elements to floor goal and partically parked in low zone.
	\item Third match. We scored climbers in autonomous and stayed in zone. In teleop we scored 13 elements to low goal and pushed buttom climber. Also we pushed our ally to the mountain. So it was able to park in low zone. In addition our ally scored 10 elements to floor goal.
\end{enumerate}
By the results of qualifying matches we became 4th. So we could choose ally for final matches. But we decided to play with team PML 30 - Y (that came 2nd) because they could push buttom climber in teleop and score debris to floor goal very fast, so we could concentrate on scoring to low box.\newline
Final matches:
\begin{enumerate}
	\item Semi final 1. We didn't score climbers in autonomous (got points only for repair zone). In teleop we scored 9 elements to low box. Our ally scored 12 elements to floor goal, pushed climber and partically parked in low zone. We scored so little debris to low box because our opponent dropped our box from the mountain and we didn't understand what should we do immediately.
	
	\item Semi final 2. We didn't score climbers in autonomous (got points only for repair zone). In teleop we scored 13 elements to low box. Our ally scored 15 elements to floor goal and pushed climber.
	
	\item Final 1. We didn't score climbers in autonomous (got points only for repair zone). In teleop we scored 12 elements to low box. Our ally scored 14 elements to floor goal and pushed climber.
	
	\item Final 2. We scored climbers in autonomous and stayed in zone. In teleop we scored 11 elements to low box. Our ally scored 12 elements to floor goal and pushed climber.
\end{enumerate} 
Summary:
\begin{enumerate}
	\item We scored to low box stably.
	
	\item Programme of autonomous period worked badly (2 times from 7 matches it worked).
	
	\item In general mechanisms worked stable. But one motor that turn lift had broken (reductor failure). Also during one match the chain fell due to collision with other robot.
\end{enumerate}
\fillpage
