\section{Business plan}
	\subsection{introduction}
	We take a responsible approach to finding sponsors, and try to spend money effectively - thinking through the details and equipment, finding ways to get the maximum benefit for the smallest cost. Some sets we received as prizes in competitions.
	
	\subsection{Our sponsors and their support}
		\subsubsection{PTC and Irisoft}
		PTC and Irisoft representative in Russia is the one company that has helped us to begin to engage FTC. They provided us our first Tetrix set within the program's Score Thehnic, which included our Lyceum. They provided us with a different command symbols plus small gifts for other teams, helped us with the delivery of details from U.S.A. We use their programa Creo for creating 3D models. We also take part in events organized by them.
		\subsubsection{Robofinist}	
		Robofinist Charitable Foundation organized by Temur Amindzhanov and by Starline. They offered us their assistance as an organization with outstanding achievements in our city. They help us financially and we recieve $2000, as well as parts and equipment from them each month.
		\subsubsection{Volnoe Delo}
		Volnoe Delo is one of the largest charitable foundations in Russia. It was established by Oleg Deripaska. We are participants of the program ROBOTOTEHNIKA. As support, they sent us free game field. They also engage in training teachers and judges, including our own. They are engage in the organization of competitions FTC in Russia and are sponsoring a trip this year's winners to St. Louis.	
		\subsubsection{Physics-Mathematics Lyceum №30}
		Physics-Mathematics Lyceum №30 is a school in which our organization is based. It provides us with a comfortable space and material assistance, as well as leaders.
		
	\subsection{Purchase of materials.}
		\subsubsection{Our method}
		When we started out in robotics, we did not have a lot of money and we used only some basic materials. Now, we have found, sponsors and firstly plan the details and equipment that we need to buy and then buy them. Such an approach allows us to find more effective solutions.
		\subsubsection{Our materials}
		We have 6 primary kits and 3 resource kits. We buy individual parts we need. At this point we have made 2 large purchases from U.S.A for $1600 in November 2014 and in March 2015.
\newpage	
